Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
conclusion to approach section

>>>>

Both of the combination methods above ($F[\cdot]$ and
$\mu_{PR}[\cdot]$) are ``naive'' combinations, in that they treat each
decomposition as equivalent to the next.  One further direction to
explore involves tuning (presumably on held-out data) the precision
and recall weights for each decomposition type for a later linear
combination.

The possible family of metrics outlined above is quite large. In the
next section, we make explicit the range of these parameters that we
explore in this article.
